---
title: "Fleet, reference table, documentation"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output: pdf_document
---



```{r setup, include = F}

library(dplyr)

dir_out <- "/output/"

```

# Data 

Input a list of all metiers used 1987-2018

```{r data, include = F}


rdb <- read.csv("Q:/mynd/SAS Library/FiskeriAktiviteter/references/RDB/AreaCodeFACCodeRegion.csv")

#A bit of renaming and deletion of id's not needed presently

rdb <- select(rename(rdb, area = AreaCode, metier_lvl6 = FishingActivityCategoryEuropeanLvl6Code), area, metier_lvl6)

dnk_metiers <- readRDS("Q:/mynd/kibi/reference_tables/fleet/dnk_metiers.rds")


metiers <- distinct(ungroup(dnk_metiers), fao_area, level_6, merged_level_6, metier_level6_ret)

```


# obs_at_sea_fleets

Relating metier level 6 and area with observer at sea fleets

Fleets for observer at-sea sampling frame: reduction_SPF, passive, outside_area_27.3-4, mussels and the rest

```{r obs_at_sea_fleets, include = F}

fleet <-
  mutate(metiers,
         obs_at_sea_fleets = ifelse(
           !(substr(fao_area, 1, 2) %in% c("27")),
           "outside_area_27.3-4",
           ifelse(
             substr(metier_level6_ret, 1, 7) == "DRB_MOL",
             "mussels",
             ifelse(
               substr(metier_level6_ret, 1, 3) %in% c(
                 "GNS",
                 "FPO",
                 "FPN",
                 "FYK",
                 "LHP",
                 "LLS",
                 "LLD",
                 "GTR",
                 "GND",
                 "MIS",
                 "LHM"
               ),
               "passive",
               ifelse(
                 substr(metier_level6_ret, 4, 6) == "SPF" |
                   substr(metier_level6_ret, 5, 7) == "SPF",
                 "reduction_SPF",
                 ifelse(
                   substr(metier_level6_ret, 5, 15) == "DEF_<16_0_0",
                   "reduction_SPF",
                   ifelse(
                     substr(metier_level6_ret, 5, 13) == "DEF_16-31",
                     "reduction_SPF",
                     ifelse(
                       substr(metier_level6_ret, 1, 7) == "TBB_DEF",
                       "TBB>120",
                       ifelse(!(
                         substr(fao_area, 1, 4) %in% c("27.3", "27.4")
                       ), "outside_area_27.3-4", "rest")
                     )
                   )
                 )
               )
             )
           )
         ))



obs_at_sea_fleets_test <-
  distinct(fleet,
           substr(fao_area, 1, 2),
           metier_level6_ret,
           obs_at_sea_fleets)               
        

```

# merged_metier

20160323: a copy from the old sas program (Matrix_Merged_level_6_Mix_WG.sas)

*Think about*

OTB_CRU_32-69 / OTB_DEF_32-69: can these be merged or are the def from SPF trips?

TBB_CRU / TBB_DEF: consider merging depending on mesh size - maybe use MCD for larger mesh sizes (equal to OTB)

Spf large meshes: A these realy targeting SPF - either wrong mesh or wrong target (going for DEF, but catching SPF)


```{r merged}


#Baltic - active - demersal

fleet_1 <-
  mutate(
    fleet,
    merged_metier_level6 = ifelse(
      substr(metier_level6_ret, 5, 20) == "DEF_90-104_0_0" &
        !(substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN")),
      "OTB_DEF_90-104_0_0",
      ifelse(
        substr(metier_level6_ret, 5, 20) == "DEF_>=105_1_110" &
          !(substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN")),
        "OTB_DEF_>=105_1_120",
        ifelse(
          substr(metier_level6_ret, 5, 20) == "DEF_>=105_1_120" &
            !(substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN")),
          "OTB_DEF_>=105_1_120",
          NA
        )
      )
    )
  )

#Baltic - active - pelagic

fleet_1 <-
  mutate(
    fleet_1,
    merged_metier_level6 = ifelse(
      substr(metier_level6_ret, 5, 14) %in% c("SPF_16-31_", "SPF_16-104", "SPF_32-89_", "SPF_32-104") &
        fao_area %in% c(
          "27.3.d.28",
          "27.3.d.28.1",
          "27.3.d.28.2",
          "27.3.d.29",
          "27.3.d.30",
          "27.3.d.31",
          "27.3.d.32"
        ),
      "OTM_SPF_16-104_0_0",
      ifelse(
        substr(metier_level6_ret, 5, 14) %in% c("SPF_32-89_", "SPF_32-104") &
          fao_area %in% c("27.3.b.23", "27.3.c.22"),
        "OTM_SPF_32-89_0_0",
        ifelse(
          substr(metier_level6_ret, 5, 14) %in% c("SPF_32-89_", "SPF_32-104") &
            fao_area %in% c("27.3.d.24", "27.3.d.25", "27.3.d.26", "27.3.d.27"),
          "OTM_SPF_32-104_0_0",
          merged_metier_level6
        )
      )
    )
  )
#North Sea, Skaggerak and Kattegat - trawlers

sk <-
  distinct(filter(fleet_1, fao_area %in% c("27.3.a.20", "27.3.a.21")), metier_level6_ret)

fleet_1 <-
  mutate(fleet_1,
         merged_metier_level6 = ifelse(
           substr(metier_level6_ret, 5, 20) %in% c("MCD_70-99_0_0", "DEF_70-99_0_0", "CRU_70-99_0_0") &
             !(
               substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN", "GNS", "TBB", "GND")
             ),
           "OTB_MCD_70-99_0_0",
           ifelse(
             substr(metier_level6_ret, 5, 20) %in% c("MCD_90-119_0_0", "DEF_90-119_0_0", "CRU_90-119_0_0") &
               !(
                 substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN", "GNS", "TBB", "GND")
               ),
             "OTB_MCD_90-119_0_0",
             ifelse(
               substr(metier_level6_ret, 5, 20) %in% c("MCD_100-119_0_0", "DEF_100-119_0_0", "CRU_100-119_0_0") &
                 !(
                   substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN", "GNS", "TBB", "GND")
                 ),
               "OTB_MCD_100-119_0_0",
               ifelse(
                 substr(metier_level6_ret, 5, 20) %in% c("MCD_>=120_0_0", "DEF_>=120_0_0", "CRU_>=120_0_0") &
                   !(
                     substr(metier_level6_ret, 1, 3) %in% c("SSC", "SDN", "GNS", "TBB", "GND")
                   ),
                 "OTB_MCD_>=120_0_0",
                 merged_metier_level6
               )
             )
           )
         ))

#North Sea, Skaggerak and Kattegat - pelagic

fleet_1 <-
  mutate(
    fleet_1,
    merged_metier_level6 = ifelse(
      substr(metier_level6_ret, 5, 14) %in% c("SPF_32-69_") &
        !(substr(fao_area, 1, 6) %in% c("27.3.b", "27.3.c", "27.3.d")) &
        substr(metier_level6_ret, 1, 2) != "PS",
      "OTM_SPF_32-69_0_0",
      merged_metier_level6
    )
  )

fleet_1 <-
  mutate(
    fleet_1,
    merged_metier_level6 = ifelse(
      substr(metier_level6_ret, 5, 14) %in% c("SPF_16-31_") &
        !(substr(fao_area, 1, 6) %in% c("27.3.b", "27.3.c", "27.3.d")) &
        substr(metier_level6_ret, 1, 2) != "PS",
      "OTM_SPF_16-31_0_0",
      merged_metier_level6
    )
  )

#All areas - demersal for reduction

fleet_1 <-
  mutate(
    fleet_1,
    merged_metier_level6 = ifelse(
      substr(metier_level6_ret, 5, 20) %in% c("DEF_<16_0_0") &
        substr(metier_level6_ret, 1, 3) %in% c("OTB", "PTB", "OTM", "PTM"),
      "OTB_DEF_<16_0_0",
      ifelse(
        substr(metier_level6_ret, 5, 20) %in% c("DEF_16-31_0_0") &
          substr(metier_level6_ret, 1, 3) %in% c("OTB", "PTB", "OTM", "PTM"),
        "OTB_DEF_16-31_0_0",
        merged_metier_level6
      )
    )
  )


test <-
  distinct(fleet_1, fao_area, metier_level6_ret, merged_metier_level6)

test_1 <-
  distinct(filter(fleet_1,!(is.na(
    merged_metier_level6
  ))),
  fao_area,
  metier_level6_ret,
  merged_metier_level6)

test_2 <-
  distinct(filter(fleet_1, is.na(merged_metier_level6)),
           fao_area,
           metier_level6_ret,
           merged_metier_level6)
```

# mixfish_fleet

20160323: a copy from the old sas program (Matrix_Merged_level_6_Mix_WG.sas)

```{r}

fleet_2 <- c()

for (i in (1:nrow(fleet_1))) {
  fleet_1 <-
    mutate(fleet_1,
           metier_in = ifelse(
             is.na(merged_metier_level6),
             metier_level6_ret ,
             merged_metier_level6
           ))
  
  fleet_i <- fleet_1[i,]
  
  if (fleet_i$fao_area %in% c("27.3.a.20", "27.3.a.21")) {
    #TBB
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "TBB_CRU_16-31_0_0",
          "TBB_CRU_16-31_0_0",
          ifelse(
            metier_in %in% c("TBB_DEF_90-119_0_0", "TBB_DEF_90-99_0_0"),
            "TBB_DEF_90-99_0_0",
            ifelse(metier_in == "TBB_DEF_>=120_0_0", "TBB_DEF_>=120_0_0", NA)
          )
        )
      )
    #OTB
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "OTB_CRU_16-31_0_0",
          "OTB_CRU_16-31_0_0",
          ifelse(
            metier_in == "OTB_CRU_32-69_0_0",
            "OTB_CRU_32-69_0_0",
            ifelse(
              metier_in == "OTM_SPF_32-69_0_0",
              "OTB_SPF_32-69_0_0",
              ifelse(
                metier_in == "PS_SPF_32-69_0_0",
                "OTB_SPF_32-69_0_0",
                ifelse(
                  metier_in == "OTB_MCD_90-119_0_0",
                  "OTB_CRU_90-119_0_0",
                  ifelse(
                    metier_in == "OTB_MCD_>=120_0_0",
                    "OTB_DEF_>=120_0_0",
                    ifelse(
                      metier_in == "OTB_CRU_70-89_2_35",
                      "OTB_CRU_70-89_2_35",
                      mixfish_fleet
                    )
                  )
                )
              )
            )
          )
        )
      )
    
    #SDN & SSC
    fleet_i <-
      mutate(fleet_i,
             mixfish_fleet = ifelse(
               metier_in %in% c("SDN_DEF_90-119_0_0", "SDN_DEF_>=120_0_0"),
               "SDN_DEF_>=120_0_0",
               ifelse(
                 metier_in %in% c("SSC_DEF_90-119_0_0", "SSC_DEF_>=120_0_0"),
                 "SSC_DEF_>=120_0_0",
                 mixfish_fleet
               )
             ))
    
    #GNS & LLS
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "GNS_DEF_100-119_0_0",
          "GNS_DEF_100-119_0_0",
          ifelse(
            metier_in == "GNS_DEF_120-219_0_0",
            "GNS_DEF_120-219_0_0",
            ifelse(
              metier_in == "GNS_DEF_>=220_0_0",
              "GNS_DEF_>=220_0_0",
              ifelse(
                substr(metier_in, 1, 3) == "LLS",
                "LLS_FIF_0_0_0",
                mixfish_fleet
              )
            )
          )
        )
      )
    
    #MIS_MIS
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          is.na(mixfish_fleet) &
            substr(metier_in, 9, 11) %in% c("16-", "<16") &
            substr(metier_in, 5, 7) != "CRU",
          "MIS_MIS_0_0_0_IBC",
          ifelse(
            is.na(mixfish_fleet) &
              !(substr(metier_in, 9, 11) %in% c("16-", "<16")),
            "MIS_MIS_0_0_0_HC",
            mixfish_fleet
          )
        )
      )
    
    
  } else if (fleet_i$fao_area %in% c("27.4.a", "27.4.b", "27.4.c", "27.7.d", "27.6.a")) {
    #TBB
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "TBB_CRU_16-31_0_0",
          "TBB_CRU_16-31_0_0",
          ifelse(
            metier_in %in% c("TBB_DEF_70-99_0_0"),
            "TBB_DEF_70-99_0_0",
            ifelse(metier_in == "TBB_DEF_>=120_0_0", "TBB_DEF_>=120_0_0", NA)
          )
        )
      )
    #OTB
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "OTB_CRU_16-31_0_0",
          "OTB_CRU_16-31_0_0",
          ifelse(
            metier_in == "OTB_CRU_32-69_0_0",
            "OTB_CRU_32-69_0_0",
            ifelse(
              metier_in == "OTM_SPF_32-69_0_0",
              "OTB_SPF_32-69_0_0",
              ifelse(
                metier_in == "PS_SPF_32-69_0_0",
                "OTB_SPF_32-69_0_0",
                ifelse(
                  metier_in == "OTB_MCD_100-119_0_0",
                  "OTB_MCD_>=120_0_0",
                  ifelse(
                    metier_in == "OTB_MCD_>=120_0_0",
                    "OTB_DEF_>=120_0_0",
                    ifelse(
                      metier_in == "OTB_MCD_70-99_0_0",
                      "OTB_CRU_70-99_0_0",
                      mixfish_fleet
                    )
                  )
                )
              )
            )
          )
        )
      )
    
    #SDN & SSC
    fleet_i <-
      mutate(fleet_i,
             mixfish_fleet = ifelse(
               metier_in %in% c("SDN_DEF_100-119_0_0", "SDN_DEF_>=120_0_0"),
               "SDN_DEF_>=120_0_0",
               ifelse(
                 metier_in %in% c("SSC_DEF_100-119_0_0", "SSC_DEF_>=120_0_0"),
                 "SSC_DEF_>=120_0_0",
                 mixfish_fleet
               )
             ))
    #GNS & LLS
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          metier_in == "GNS_DEF_90-99_0_0",
          "GNS_DEF_100-119_0_0",
          ifelse(
            metier_in == "GNS_DEF_100-119_0_0",
            "GNS_DEF_100-119_0_0",
            ifelse(
              metier_in == "GNS_DEF_120-219_0_0",
              "GNS_DEF_120-219_0_0",
              ifelse(
                metier_in == "GNS_DEF_>=220_0_0",
                "GNS_DEF_>=220_0_0",
                ifelse(
                  substr(metier_in, 1, 3) == "LLS",
                  "LLS_FIF_0_0_0",
                  ifelse(
                    metier_in == "FPO_CRU_0_0_0",
                    "FPO_CRU_0_0_0",
                    mixfish_fleet
                  )
                )
              )
            )
          )
        )
      )
    
    #MIS_MIS
    fleet_i <-
      mutate(
        fleet_i,
        mixfish_fleet = ifelse(
          is.na(mixfish_fleet) &
            substr(metier_in, 9, 11) %in% c("16-", "<16") &
            substr(metier_in, 5, 7) != "CRU",
          "MIS_MIS_0_0_0_IBC",
          ifelse(
            is.na(mixfish_fleet) &
              !(substr(metier_in, 9, 11) %in% c("16-", "<16")),
            "MIS_MIS_0_0_0_HC",
            mixfish_fleet
          )
        )
      )
    
    
  }
  fleet_2 <- select(bind_rows(fleet_2, fleet_i), -metier_in)
}

test <-
  distinct(filter(fleet_2, fao_area %in% c("27.3.a.20", "27.3.a.21")),
           metier_level6_ret,
           mixfish_fleet)
test_2 <-
  distinct(filter(
    fleet_2,
    fao_area %in% c("27.4.a", "27.4.b", "27.4.c", "27.7.d", "27.6.a")
  ),
  metier_level6_ret,
  mixfish_fleet)


```


# wgbfas_fleet

```{r wgbfas}

```


```{r output, include = F}

matrix_out <-
  distinct(
    fleet_2,
    fao_area,
    metier_level6_ret,
    obs_at_sea_fleets,
    merged_metier_level6,
    mixfish_fleet
  )
matrix_out <- rename(matrix_out, metier_level6 = metier_level6_ret)

saveRDS(matrix_out, "fleet.rds")
write.csv(matrix_out, "fleet.csv", row.names = F)

```


